|

### 2022-11-09 manuscript.Rmd
fix typos in intro

Despite the increasing demand for accessibility knowledge in both industries and academia and the critical impact of accessible visualizations, accessibility has not yet found its place in the data science course and teaching materials. One main reason for this could be that accessibility is often incorporated into human-computer interaction (HCI) and design courses [@shinoharaHowDesigningPeople2016; @shinoharaTeachingAccessibilityTechnology2017a], introductory web development [@koAccessComputingPromotesTeaching2016; @rosmaitaAccessibilityFirstNew2006], software engineering courses [@martin-escalonaIntroductionTopicAccessibility2013; @ludiIntroducingAccessibilityRequirements2007; @ludiAccessEveryoneIntroducing2002] or the digital arts [@barata2019inclusion], if at all covered. However, data science is an interdisciplinary field that is taught in various disciplines, including not only computer and information sciences but also statistics, business schools, political science, biological sciences, and more [@schwab2021data]. Therefore, we posit that the resources and conversations around accessibility have not yet extended to the broader data science education community at the scale that they should. For instance, many introductory data science courses [@yan2019first; @baumer2015data], textbooks [@adhikari2019computational; @wickham2016r], or curricula [@schwab2021data] either fail to mention accessibility at all or only focus on the accessing data.

>>>>

Despite the increasing demand for accessibility knowledge in both industries and academia and the critical impact of accessible visualizations, accessibility has not yet found its place in the data science course and teaching materials. One main reason for this could be that accessibility is often incorporated into human-computer interaction (HCI) and design courses [@shinoharaHowDesigningPeople2016; @shinoharaTeachingAccessibilityTechnology2017a], introductory web development [@koAccessComputingPromotesTeaching2016; @rosmaitaAccessibilityFirstNew2006], software engineering courses [@martin-escalonaIntroductionTopicAccessibility2013; @ludiIntroducingAccessibilityRequirements2007; @ludiAccessEveryoneIntroducing2002] or the digital arts [@barata2019inclusion], if at all covered. However, data science is an interdisciplinary field that is taught in various disciplines, including not only computer and information sciences but also statistics, business schools, political science, biological sciences, and more [@schwab2021data]. Therefore, we posit that the resources and conversations around accessibility have not yet extended to the broader data science education community at the scale that they should. For instance, many introductory data science courses [@yan2019first; @baumer2015data], textbooks [@adhikari2019computational; @wickham2016r], or curricula [@schwab2021data] either fail to mention accessibility at all or only focus on accessing the data.
